Supplement 3.2 and 3.3

### 2023-12-21 Code/Supplement 1B_figures.Rmd
updated figure legends and text

## Change labels for counties
 rename_counts <-function(df) {   
   df <-df %>%
     mutate(pop_size_quant2=ifelse(pop_size_quant2==1, "County Forecasts: Size Quantile 1",
                                 ifelse(pop_size_quant2==2, "County Forecasts: Size Quantile 2",
                                        ifelse(pop_size_quant2==3, "County Forecasts: Size Quantile 3", 
                                               ifelse(pop_size_quant2==4, "County Forecasts: Size Quantile 4", "County forecasts: Size Quantile 5")))))
}

@@

####
load(here("Data/cases_county_forecasts_2022-04-04.Rdata"))
size <-read.csv(here("Data/SVI2018_US_COUNTY.csv")) %>%
  dplyr::select(FIPS, E_TOTPOP) %>%
  rename(location=FIPS) %>%
  mutate(location=as.character(location),
         location=ifelse(nchar(location)==4, paste0("0", location), location),
         pop_size_quant2=cut(E_TOTPOP, breaks = quantile(E_TOTPOP, probs = seq(0, 1, 0.20)),
                             include.lowest = TRUE, labels = 1:5)
  ) %>% 
  dplyr::select(-E_TOTPOP) 
all_dat <-all_dat %>% left_join(., size, by="location") 
rm(size)
counts <-all_dat %>%
  filter(!(model %in% sec_models),
         sub_date >= start_date & sub_date <= stop_date) %>%
  filter(type=="point")

>>>>

## Change labels for counties
 rename_counts <-function(df) {   
   df <-df %>%
     mutate(pop_size_quant2=ifelse(pop_size_quant2==1, "County Forecasts: Size Quintile 1",
                                 ifelse(pop_size_quant2==2, "County Forecasts: Size Quintile 2",
                                        ifelse(pop_size_quant2==3, "County Forecasts: Size Quintile 3", 
                                               ifelse(pop_size_quant2==4, "County Forecasts: Size Quintile 4", "County forecasts: Size Quintile 5")))))
}

@@

####
load(here("Data/Submitted_cases_county_forecasts.Rdata"))
size <-read.csv(here("Data/SVI2018_US_COUNTY.csv")) %>%
  dplyr::select(FIPS, E_TOTPOP) %>%
  rename(location=FIPS) %>%
  mutate(location=as.character(location),
         location=ifelse(nchar(location)==4, paste0("0", location), location),
         pop_size_quant2=cut(E_TOTPOP, breaks = quantile(E_TOTPOP, probs = seq(0, 1, 0.20)),
                             include.lowest = TRUE, labels = 1:5)
  ) %>% 
  dplyr::select(-E_TOTPOP) 
all_dat <-all_dat %>% left_join(., size, by="location") 
rm(size)
counts <-all_dat %>%
  filter(!(model %in% sec_models),
         sub_date >= start_date & sub_date <= stop_date) %>%
  filter(type=="point")

### 2023-12-21 Code/Supplement 3.1_figure.rmd
updated figure legends and text

  WIS_counties <-WIS_all %>%
    filter(type=="quantile") %>%
    summarise_scores(by = c("model"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill) %>%
    distinct() %>%
    mutate(pop_size_quant2="County Forecasts: Size Quantile 5",
           model_reorder=fct_reorder(model, scaled_rel_skill))
  levels_model <-levels(WIS_counties$model_reorder)

@@

  WIS_counties_other <-WIS_all %>%
    filter(type=="quantile") %>%
    summarise_scores(by = c("model", "pop_size_quant2"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill, pop_size_quant2) %>%
    distinct() %>%
    rename_counts() %>%
    add_row(model="FRBSF_Wilson-Econometric", pop_size_quant2="County Forecasts: Size Quantile 1") %>% #,
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 1") %>% #, 
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 2") %>% #, 
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 3") %>% #, 
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quantile 4") %>% 
    mutate(model_reorder=model) %>%
    mutate(model_reorder=factor(model, levels_model))

@@

  ## Large counties
  coverage_counties <- dat_large_count %>%
    filter(sub_date <= cut_date) %>%
    coverage(df=.) %>%
    group_by(model) %>%
    summarize(mean_count=mean(coverage.95)) %>%
    mutate(pop_size_quant2="County Forecasts: Size Quantile 5")

@@

  cov.95 <-coverage_counties %>%
    bind_rows(., coverage_counties_other) %>%
    mutate(value_display=format(round(mean_count, digits=2), nsmall = 2),
           value_display=ifelse(value_display=="  NA", NA, value_display))
}
cov.95 <-cov.95() %>%
  rename_counts() %>%
  ungroup() %>%
  mutate(key=pop_size_quant2) %>%
  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quantile 1") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 1") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 2") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 3") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 4") %>%
  mutate(model_reorder=factor(model, levels_model))

@@

load(here("Data/cases_large counties_forecasts_for analysis.rdata"))
subs_co <-submissions(df=dat_large_count) %>%
  mutate(pop_size_quant2="County Forecasts: Size Quantile 5")

@@

all_subs <-subs_co %>%
  bind_rows(., subs_co_other) %>%
  mutate(key=pop_size_quant2,
         value_display=format(round(per_sub, digits=2), nsmall = 2),
         value_display=ifelse(value_display=="  NA", NA, value_display)) %>%
  ungroup() %>%
  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quantile 1") %>%  
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 1") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 2") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 3") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quantile 4") %>%
  mutate(model_reorder=factor(model, levels_model)) %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=per_sub)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient(low = "#fde0dd", high = "#c51b8a", na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="% Weeks \nSubmitted",
       title="A. Percent of Weeks Submitted") +
  theme(axis.title.x = element_blank(),   
        axis.title.y = element_blank(), 
        axis.text=axis.text_standard,
        legend.position="bottom")

>>>>

  WIS_counties <-WIS_all %>%
    filter(type=="quantile") %>%
    summarise_scores(by = c("model"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill) %>%
    distinct() %>%
    mutate(pop_size_quant2="County Forecasts: Size Quintile 5",
           model_reorder=fct_reorder(model, scaled_rel_skill))
  levels_model <-levels(WIS_counties$model_reorder)

@@

  WIS_counties_other <-WIS_all %>%
    filter(type=="quantile") %>%
    summarise_scores(by = c("model", "pop_size_quant2"),
                     metric="interval_score",
                     relative_skill = TRUE,
                     baseline = "COVIDhub-baseline") %>%
    dplyr::select(model, scaled_rel_skill, pop_size_quant2) %>%
    distinct() %>%
    rename_counts() %>%
    add_row(model="FRBSF_Wilson-Econometric", pop_size_quant2="County Forecasts: Size Quintile 1") %>% #,
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quintile 1") %>% #, 
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quintile 2") %>% #, 
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quintile 3") %>% #, 
    add_row(model="UMass-MechBayes", pop_size_quant2="County Forecasts: Size Quintile 4") %>% 
    mutate(model_reorder=model) %>%
    mutate(model_reorder=factor(model, levels_model))

@@

  ## Large counties
  coverage_counties <- dat_large_count %>%
    filter(sub_date <= cut_date) %>%
    coverage(df=.) %>%
    group_by(model) %>%
    summarize(mean_count=mean(coverage.95)) %>%
    mutate(pop_size_quant2="County Forecasts: Size Quintile 5")

@@

  cov.95 <-coverage_counties %>%
    bind_rows(., coverage_counties_other) %>%
    mutate(value_display=format(round(mean_count, digits=2), nsmall = 2),
           value_display=ifelse(value_display=="  NA", NA, value_display))
}
cov.95 <-cov.95() %>%
  rename_counts() %>%
  ungroup() %>%
  mutate(key=pop_size_quant2) %>%
  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quintile 1") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 1") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 2") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 3") %>% #, 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 4") %>%
  mutate(model_reorder=factor(model, levels_model))

@@

load(here("Data/cases_large counties_forecasts_for analysis.rdata"))
subs_co <-submissions(df=dat_large_count) %>%
  mutate(pop_size_quant2="County Forecasts: Size Quintile 5")

@@

all_subs <-subs_co %>%
  bind_rows(., subs_co_other) %>%
  mutate(key=pop_size_quant2,
         value_display=format(round(per_sub, digits=2), nsmall = 2),
         value_display=ifelse(value_display=="  NA", NA, value_display)) %>%
  ungroup() %>%
  add_row(model="FRBSF_Wilson-Econometric", key="County Forecasts: Size Quintile 1") %>%  
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 1") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 2") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 3") %>% 
  add_row(model="UMass-MechBayes", key="County Forecasts: Size Quintile 4") %>%
  mutate(model_reorder=factor(model, levels_model)) %>%
  ggplot(., aes(key, model_reorder)) +
  geom_tile(aes(fill=per_sub)) +
  geom_text(aes(label=value_display), size=3.5) +
  scale_fill_gradient(low = "#fde0dd", high = "#c51b8a", na.value = "grey75") + 
  scale_x_discrete(labels = function(x) str_wrap(x, width=15)) +
  theme_bw() +
  labs(fill="% Weeks \nSubmitted",
       title="A. Percent of Weeks Submitted") +
  theme(axis.title.x = element_blank(),   
        axis.title.y = element_blank(), 
        axis.text=axis.text_standard,
        legend.position="bottom")

### 2023-12-21 Code/Supplement 3.2 and 3.3_figures.rmd
updated figure legends and text

### WIS Over time
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/WIS_all horizons_non large counties_all subs.rdata")

@@

### Coverage Over time
load("C:/Users/oko8/OneDrive - CDC/COVID/Forecasts/Data/cases_non large counties_forecasts_for analysis_2022-08-18.Rdata")

@@

p1 <-cov.plot(coverage_count1, labels_count1) +
  labs(title="County Forecasts: Size Quantile 1") +
  theme(legend.position = c(0.02, 0.88), legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.5,1,1,1)),
        legend.key = element_rect(colour = NA, fill = NA))

coverage_count2 <-cov.fig_dat(filter(dat_other_count, pop_size_quant2==2, sub_date <= stop_date))
labels_count2 <-data_labels(coverage_count2) 
p2 <-cov.plot(coverage_count2, labels_count2) +
  labs(title="County Forecasts: Size Quantile 2", 
       y="")

coverage_count3 <-cov.fig_dat(filter(dat_other_count, pop_size_quant2==3, sub_date <= stop_date))
labels_count3 <-data_labels(coverage_count3) 
p3 <-cov.plot(coverage_count3, labels_count3) +
  labs(title="County Forecasts: Size Quantile 3",
       x="Expected Coverage")

coverage_count4 <-cov.fig_dat(filter(dat_other_count, pop_size_quant2==4, sub_date <= stop_date))
labels_count4 <-data_labels(coverage_count4) 
p4 <-cov.plot(coverage_count4, labels_count4) +
  labs(title="County Forecasts: Size Quantile 4",
       y="",
       x="Expected Coverage")

>>>>

### WIS Over time
load(here("Data/WIS_all horizons_non large counties.rdata"))

@@

### Coverage Over time
load(here("Data/cases_non large counties_forecasts_for analysis.rdata"))

@@

p1 <-cov.plot(coverage_count1, labels_count1) +
  labs(title="County Forecasts: Size Quintile 1") +
  theme(legend.position = c(0.02, 0.88), legend.title = element_blank(),
        legend.justification = c(0, 0.5), 
        legend.margin=margin(c(0.5,1,1,1)),
        legend.key = element_rect(colour = NA, fill = NA))

coverage_count2 <-cov.fig_dat(filter(dat_other_count, pop_size_quant2==2, sub_date <= stop_date))
labels_count2 <-data_labels(coverage_count2) 
p2 <-cov.plot(coverage_count2, labels_count2) +
  labs(title="County Forecasts: Size Quintile 2", 
       y="")

coverage_count3 <-cov.fig_dat(filter(dat_other_count, pop_size_quant2==3, sub_date <= stop_date))
labels_count3 <-data_labels(coverage_count3) 
p3 <-cov.plot(coverage_count3, labels_count3) +
  labs(title="County Forecasts: Size Quintile 3",
       x="Expected Coverage")

coverage_count4 <-cov.fig_dat(filter(dat_other_count, pop_size_quant2==4, sub_date <= stop_date))
labels_count4 <-data_labels(coverage_count4) 
p4 <-cov.plot(coverage_count4, labels_count4) +
  labs(title="County Forecasts: Size Quintile 4",
       y="",
       x="Expected Coverage")
